\CVSectionHeader{Experiences}
\TitledListBegin{
  \TitleWithPeriod{\textbf{Tech Leader}, Gogifarm Co. South Korea}{Sep. 2024}[Present]
}
  \TitledListItem{Led the design and implementation of the company's overall system architecture, including CI/CD pipelines and scalable deployment infrastructure.}
  \TitledListItem{Developed a full-stack web platform featuring user authentication (OAuth 2.0), integrated payment services, and admin dashboards using AWS, Kubernetes, Kotlin, Node.js, Next.js, and Spring Boot.}
  \TitledListItem{Maintained a robust and highly available backend system, while optimizing the frontend for responsiveness and performance.}
  \TitledListItem{Collaborated with designers to evaluate and improve UI/UX, enhancing accessibility and usability across devices.}
\TitledListEnd
\vspace{1em}
\TitledListBegin{
  \TitleWithPeriod{\textbf{Robotics software \& Platform engineer}, Floatic Co. South Korea}{Jun. 2022}[Sep. 2024]
}
  \TitledListItem{Developed ROS2-based low-level sensor drivers, including IMU, motor controllers, and LiDAR, ensuring reliable communication and integration.}
  \TitledListItem{Designed and optimized the full-stack navigation pipeline using ROS2 Navigation2, including path planning, controller tuning, and behavior tree structures.}
  \TitledListItem{Architected robust communication middleware between robots and cloud backend using Kafka and MQTT supporting scalable\\bi-directional data exchange.}
  \TitledListItem{Built internal infrastructure for robotic DevOps, including private APT package server and automated CI/CD pipeline.}
  \TitledListItem{Utilized NVIDIA Isaac Sim and AWS RoboMaker for cloud-based simulation, testing, and deployment of multi-robot systems.}
\TitledListEnd
\vspace{1em}
\TitledListBegin{
  \TitleWithPeriod{\textbf{Research assistant}, Hanyang University ERICA}{Dec. 2019}[Jul. 2021]
}
  \TitledListItem{Collaborated with master's. students on diverse robotics research projects, contributing to system implementation, testing, and troubleshooting.}
  \TitledListItem{Led the development of vision algorithms for a furniture assembly robot, focusing on precise object localization in complex environments.}
  \TitledListItem{Took part in multiple industry-academia collaborative research efforts, working on motion sensing, computer vision, and mobile robot systems.}
  \TitledListItem{Actively participated in internal robotics theory study groups, leading sessions and discussing recent publications with lab members.}
  \TitledListItem{Prepared and delivered lectures for undergraduate robotics courses, including content planning, slide design, and hands-on lab instruction.}
\TitledListEnd
\vspace{1em}
\TitledListBegin{
  \TitleWithPeriod{\textbf{Collaborative Robot Design Teaching Assistant}, Hanyang University ERICA}{Fall. 2020}
}
  \TitledListItem{Developed lecture materials and led practical sessions for a project-based course on collaborative robotics using the UR5 robot.}
  \TitledListItem{Guided students in implementing socket-based TCP communication protocols for robot control and data exchange.}
  \TitledListItem{Assisted students in understanding key principles of human-robot collaboration through hands-on robot programming and system integration.}
\TitledListEnd
\vspace{1em}
\TitledListBegin{
  \TitleWithPeriod{\textbf{Introduction to Robotics Design Teaching assistant}, Hanyang University ERICA}{Spring. 2020}
}
  \TitledListItem{Assisted in teaching a hands-on introductory robotics course covering basic electronics, sensors, filtering algorithms, and robot design.}
  \TitledListItem{Guided students through Arduino-based circuit building, sensor integration, and control implementation.}
  \TitledListItem{Supervised students in 3D modeling and printing for robot prototyping, followed by Raspberry Pi-based robot system development.}
\TitledListEnd
