\CVSectionHeader{Research \&\\Engineering Focus}
\CVSectionListBegin
  \CVSectionListItem{Multi-Robot Navigation \& Multi-Agent Path Finding (warehouse, smart-farm)}
  \CVSectionListItem{System Architecture \& Fleet Management (ROS2, Kafka/MQTT, CI/CD)}
  \CVSectionListItem{Perception \& Control (pose estimation, sensor fusion, controller tuning)}
\CVSectionListEnd
\vspace{1em}

\CVSectionHeader{Education}
\TitleWithPeriodAndSub{
  \textbf{Hanyang University ERICA} \\
  B.S. in Robotics Engineering | \small{GPA: 3.69 / 4.5 (Major: 3.92 / 4.5)}\\
  \textbf{Graduation Project:} Automotive Marine Rescue Robot
}{Ansan, Republic of Korea}{Mar 2016}[Feb 2023][0.7]
\vspace{1em}

\CVSectionHeader{Work\\Experience}

\vspace{1em}
\TitleWithPeriodAndSub{
  \Large\textbf{Metafarmers Co.} \href{https://metafarmers.ai/}{\small\textcolor{gray}{\faGlobe} site} \\[0.3em]
  \small\textit{MetaFarmers automates repetitive, skilled tasks using AI and robotics to sustainable agriculture.}
}{Seoul, Republic of Korea}{Sep 2025}[Present][0.7]

\vspace{1em}
\begin{minipage}[t]{0.2\linewidth}
  \noindent
  \textbf{Robotics AI\\Team Lead}
\end{minipage}
\hspace{0.25em}
\begin{minipage}[t]{\dimexpr\linewidth-0.2\linewidth-0.25pt\relax}
  \TitledListBegin{
    \textbf{Leading and Building Robotics AI Team.}
  }
    \TitledListItem{\small Defined milestones and detailed task plans for the robotics AI team.}
    \TitledListItem{\small Established coding standards, development workflows, and quality assurance strategies.}
  \TitledListEnd

  \vspace{0.5em}
  \TitledListBegin{
    \textbf{Developing Autonomous Robot Navigation in Smart Farms.}
  }
    \TitledListItem{\small Specifying localization requirements and navigation capabilities for diverse farm environments.}
    \TitledListItem{\small Implementing end-to-end navigation systems enabling fully autonomous field operations.}
  \TitledListEnd

  \vspace{0.5em}
  \TitledListBegin{
    \textbf{Architecting Multi Robot Management System and Infrastructure.}
  }
    \TitledListItem{\small Designing system architecture for monitoring robot states and coordinating task execution.}
    \TitledListItem{\small Developing data pipelines supporting multi-robot navigation and large-scale data collection.}
  \TitledListEnd
\end{minipage}

\vspace{2em}
\TitleWithPeriodAndSub{
  \Large\textbf{Floatic Co.}\\[0.3em]
  \small\textit{A warehouse automation solutions provider developing AMRs and a real-time management platform.}
}{Seoul, Republic of Korea}{Jul 2022}[Sep 2024][0.7]

\vspace{1em}
\begin{minipage}[t]{0.2\linewidth}
  \noindent
  \textbf{Robotics\\Software Engineer}
\end{minipage}%
\hspace{0.25em}%
\begin{minipage}[t]{\dimexpr\linewidth-0.2\linewidth-0.25pt\relax}%
  \TitledListBegin{
    \textbf{Designed Multi-Robot Navigation Systems for Logistic Warehouses.}
  }
    \TitledListItem{
      \small{Designed decentralized, prioritized multi-robot navigation using a topology-based routing system.}
    }
    \TitledListItem{
      \small{Developed path planners and custom costmap layers to handle unidirectional path constraints.}
    }
    \TitledListItem{
      \small{Customized local controllers and optimized control parameters for single-robot navigation.}
    }
  \TitledListEnd

  \vspace{0.5em}
  \TitledListBegin{
    \textbf{Built a System Architecture for Robot Software.}
  }
    \TitledListItem{
      \small{Designed robot software architecture and maintained code quality.}
    }
    \TitledListItem{
      \small{Implemented and maintained CI/CD pipelines for robotic software.}
    }
  \TitledListEnd

\end{minipage}

\vspace{1.5em}
\begin{minipage}[t]{0.2\linewidth}
  \noindent
  \textbf{Robotics\\Platform Engineer}
\end{minipage}
\hspace{0.25em}
\begin{minipage}[t]{\dimexpr\linewidth-0.2\linewidth-0.25pt\relax}
  \TitledListBegin{
    \textbf{Developed middleware connecting robots with backend and frontend applications.}
  }
    \TitledListItem{
      \small{Designed middleware systems with high modularity using message brokers (e.g., Kafka, MQTT).}
    }
    \TitledListItem{
      \small{Defined robot states, behavior strategies, and task flows.}
    }
  \TitledListEnd  
\end{minipage}

