\CVSectionHeader{Experiences}
% \TitledListBegin{
%   \TitleWithPeriod{\textbf{Tech Leader}, Gogifarm Co. South Korea}{2024}[Present]
% }
%   \TitledListItem{Designed and implemented application's architecture and business model}
% \TitledListEnd
% \vspace{1em}
\TitledListBegin{
  \TitleWithPeriod{\textbf{Robotics Software \& Platform Engineer, Floatic Co. Korea}}{2022}[2024]
}
  \TitledListItem{Developed and optimized production-grade navigation pipelines using ROS2 (path planning, local controllers, behavior trees) for autonomous warehouse robots.}
  \TitledListItem{Built ROS2-based drivers and middleware for hardware integration (LiDAR, IMU, motor controllers) and inter-module communication.}
  \TitledListItem{Implemented fleet supervision and backend–robot communication layers using Redis, Kafka, and MQTT for scalable multi-robot operation.}
  \TitledListItem{Connected robot data streams with company back-office systems, improving monitoring, operator interaction, and deployment efficiency.}
  \TitledListItem{Established internal DevOps infrastructure (private APT repositories, CI/CD pipelines) and engaged with AWS engineers to evaluate cloud-based simulation (RoboMaker) for scalable multi-robot deployment.}
\TitledListEnd
\vspace{1em}
\TitledListBegin{
  \TitleWithPeriod{\textbf{Tutoring Mentor – Computer Architecture, Hanyang University ERICA}}{Spring. 2021}
}
  \TitledListItem{Provided academic support in processor design and RISC-V assembly through one-on-one tutoring and group sessions}
\TitledListEnd
\vspace{1em}
\TitledListBegin{
  \TitleWithPeriod{\textbf{Research Assistant, Hanyang University ERICA}}{2019}[2021]
}
  \TitledListItem{Participated in national and industry–academia robotics projects, including the \textit{Item Assembly AI Robot Challenge} (Ministry of Science and ICT) and defect inspection software development with UNIEYE Co., focusing on perception algorithms, camera calibration, and system integration.}
  \TitledListItem{Supported graduate students’ research by assisting with system implementation, debugging, and experimental validation, while developing embedded firmware for low-level sensor and motor control on MCUs.}
  \TitledListItem{Developed and maintained ROS drivers for motion capture systems (e.g., OptiTrack) and transferred related technical packages to industry partners.}
\TitledListEnd
\vspace{1em}
\TitledListBegin{
  \TitleWithPeriod{\textbf{Collaborative Robot Design Teaching Assistant, Hanyang University ERICA}}{Fall 2020}
}
  \TitledListItem{Prepared and delivered lectures on UR5 manipulation, including MoveIt API and human–robot collaboration concepts.}
  \TitledListItem{Led project-based labs where students implemented TCP socket control and collaborative task execution.}
\TitledListEnd
\vspace{1em}
\TitledListBegin{
  \TitleWithPeriod{\textbf{Introduction to Robotics Design Teaching Assistant, Hanyang University ERICA}}{Spring 2020}
}
  \TitledListItem{Developed course modules covering Arduino/Raspberry Pi programming, sensor integration, filtering, and control implementation.}
  \TitledListItem{Supervised hands-on prototyping: circuit building, 3D modeling/printing, and robot system assembly.}
\TitledListEnd
