\CVSectionHeader{Research \&\\Development Projects}
\TitleWithPeriodAndSub{
  \textbf{Omni Farmer}\\[0.1em]
  \small\textit{Agricultural Robot for harvesting, sorting, and smart farm automation.}
}{\textbf{Industrial Robotics, Metafarmers Co.}}{2025}[Present][0.65]
\CVSectionListBegin
  \CVSectionListItem{\textasciitilde\$2.3M USD venture-funded project deploying fleets of robots in a 1.65-hectare (\textasciitilde16,500 m$^2$) smart farm.}
  \CVSectionListItem{Investigating multi-robot coordination strategies for large-scale agricultural fleets, focusing on congestion mitigation and communication efficiency.}
  \CVSectionListItem{Analyzing navigation reliability under irregular terrain and unstructured farm layouts to develop robust path planning heuristics.}
  \CVSectionListItem{Designing and validating integrated navigation–manipulation–perception pipelines to improve multi-robot adaptability in dynamic field conditions.}
  \CVSectionListItem{Targeting 90\%+ automated harvesting and pollination success while enabling yield prediction and region-based harvesting recommendations.}
  \CVSectionListItem{Formulating maintainable deployment pipelines for iterative field experiments across multi-robot systems.}
\CVSectionListEnd

\vspace{0.5em}
\TitleWithPeriodAndSub{
  \textbf{Floady} ~~ \href{https://www.youtube.com/watch?v=0acR1xwGQf8}{\textcolor{red}{\faYoutube} youtube}\\[0.1em]
  \small\textit{Autonomous Mobile Robot for Warehouses, assisting workers and improving productivity.}
}{\textbf{Industrial Robotics, Floatic Co.}}{2022}[2024]
\CVSectionListBegin
  \CVSectionListItem{\textasciitilde \$8M USD venture-funded project on autonomous warehouse robots.}
  \CVSectionListItem{Deployed 10+ robots in a live warehouse (300+ hours), achieving ~90\% navigation success and >95\% task completion.}
  \CVSectionListItem{Explored decentralized multi-agent navigation algorithms to alleviate congestion and deadlocks in dense warehouse environments.}
  \CVSectionListItem{Evaluated topology-graph-based routing strategies through over 300 hours of live fleet deployment, achieving measurable improvements in throughput and fairness.}
  \CVSectionListItem{Formulated a fleet-level coordination layer integrating task allocation, monitoring, and flow optimization, forming the basis for follow-up MAPF research.}
  \CVSectionListItem{Established internal DevOps pipelines (APT repositories, CI/CD).}
\CVSectionListEnd

\vspace{0.5em}
\TitleWithPeriodAndSub{
  \textbf{Capstone Design} ~~ \href{https://www.youtube.com/watch?v=0acR1xwGQf8}{\textcolor{red}{\faYoutube} youtube}\\[0.1em]
  \small\textit{Automotive marine rescue robot}
}{\textbf{Capstone, Hanyang University ERICA}}{2020}[2022][0.3]
\CVSectionListBegin
  \CVSectionListItem{Capstone project with a budget of \textasciitilde \$12K USD, funded through competition awards and external support.}
  \CVSectionListItem{Achieved 80\% success rate in controlled pool environments, with 6–8 m drowning-person detection and real-time notification via web-based map API.}
  \CVSectionListItem{Studied control stability and responsiveness in waterborne rescue robots using PID-based navigation tuning.}
  \CVSectionListItem{Evaluated sensor fusion techniques (Kalman, low-pass filtering) for reliable pose estimation under dynamic water disturbances.}
  \CVSectionListItem{Achieved efficient onboard processing by splitting computation between Jetson Nano (YOLOv5-based detection, 3–7 Hz) and Raspberry Pi (state estimation and control).}
\CVSectionListEnd

\vspace{0.5em}
\TitleWithPeriodAndSub{
  \textbf{LattePanda} ~~ \href{https://www.youtube.com/watch?v=2ig5qAAA0DM&t=62s}{\textcolor{red}{\faYoutube} youtube}\\[0.1em]
  \small\textit{Donation \& Recycling Robot}
}{\textbf{Course Work, Hanyang University ERICA}}{2020}[][0.3]
\CVSectionListBegin
  \CVSectionListItem{Course-funded project (~\$0.8K USD per 4-6 member team) to design a mobile service robot encouraging recycling and donations in public spaces.}
  \CVSectionListItem{Led system design of a mobile service robot that encouraged recycling and donations in public open spaces, combining navigation, perception, and human–robot interaction.}
  \CVSectionListItem{Proposed and tested a lightweight obstacle-avoidance method using segmented RealSense depth data and weighted heuristics for low-cost service robots.}
  \CVSectionListItem{Implemented YOLOv4-based perception with SORT tracking, detecting individuals carrying disposable cups with >90\% accuracy.}
  \CVSectionListItem{Built ROS pipeline, motor control via PID, and PyQt/OpenCV UI that delivered engaging environmental animations and panda-robot gestures.}
\CVSectionListEnd

\vspace{0.5em}
\TitleWithPeriodAndSub{
  \textbf{Item Assembly AI Robot Challenge in Ministry of Science and ICT Korea}\\[0.em]
  \small\textit{Developing robots that recognize and assemble items.}
}{\textbf{Vision Research, AIRO LAB}}{2020}[][0.6]
\CVSectionListBegin
  \CVSectionListItem{Investigated pose estimation accuracy for robotic assembly tasks using vision-based keypoint alignment, contributing to a national multi-lab benchmark.}
\CVSectionListEnd

\vspace{0.5em}
\TitleWithPeriodAndSub{
  \textbf{Churo} ~~ \href{http://www.roboicorp.com/sub/develop/churo2.php}{\textcolor{gray}{\faGlobe} site}\\[0.1em]
  \small\textit{Dog-care robot, detecting dogs and recognizing behavioral patterns.}
}{\textbf{Independent Contract, ROBOI Co., South Korea}}{2020}[][0.5]
\CVSectionListBegin
  \CVSectionListItem{\$25K independent contract project developing a dog-care robot.}
  \CVSectionListItem{Implemented YOLOv5-based dog detection with $\sim$95\% accuracy.}
  \CVSectionListItem{Trained an LSTM model for behavior pattern recognition, achieving $\sim$75\% classification accuracy.}
  \CVSectionListItem{Designed TCP-based image streaming between edge device and AWS server, achieving $\sim$0.3s latency with inference performed in the cloud.}
\CVSectionListEnd

